A sheaf--function dictionary for algebraic tori over non-archimedean local fields

### 2013-08-16 shanghai.tex
Fixing h and h' in Transfer section

One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between
$\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}; let $h'$ be this quantity for $T'$.
Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$, 
\Clifton{Is this correct?}
then there is a canonical isomorphism of smooth group schemes
 \[
  \TT_{N-3h} \to \TT'_{N-3h}
 \]
 determined by $\alpha, \beta$ and $\phi$.
Combining this with Theorem \ref{thm:application} gives the geometrization and categorification of the transfer of characters.

\begin{corollary}\label{cor:transfer}
 With notation above, suppose that $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$.  Set $d = N-3h$.
 Then there is a canonical equivalence of categories
 \[
  \QC(\GN{T}'_{d}) \to \QC(\GN{T}_{d})
 \]
 determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
 \[
  \Hom_{<d}(T'(K'), \EEx) \to \Hom_{<d}(T(K), \EEx)
 \]
 through the trace of Frobenius.
\end{corollary}

>>>>

One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between
$\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}.
Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $N > 3h$ and $T$ and $T'$ are $N$-congruent 
then there is a canonical isomorphism of smooth group schemes
 \[
  \TT_{N-3h} \to \TT'_{N-3h}
 \]
 determined by $\alpha, \beta$ and $\phi$.
Combining this with Theorem \ref{thm:application} gives the geometrization and categorification of the transfer of characters.

\begin{corollary}\label{cor:transfer}
 With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $d = N-3h$.
 Then there is a canonical equivalence of categories
 \[
  \QC(\GN{T}'_{d}) \to \QC(\GN{T}_{d})
 \]
 determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
 \[
  \Hom_{<d}(T'(K'), \EEx) \to \Hom_{<d}(T(K), \EEx)
 \]
 through the trace of Frobenius.
\end{corollary}
